Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2020-01-30 doc/Paper/main.tex
Addressed photoz comment.

  \subsubsection{Photometric redshift systematics modeling}\label{sssec:methods.theory.photoz_syst}
    Uncertainties in photometric redshifts represent one of the major systematic uncertainties in photometric galaxy clustering analyses. To lowest order, errors in photo-$z$'s cause shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies. In this work, we therefore choose to parametrize the impact of photo-$z$ errors on the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by
    \begin{equation}
      p_{i}(z) \propto \hat{p}_{i}(z_{c} + (1 + z_{w, i})(z-z_{c}) + \Delta z_{i}),
      \label{eq:photo-z-model}
    \end{equation} 
    where the index $i$ runs over the number of redshift bins considered in our analysis. In the above equation, $\hat{p}_{i}(z)$ denotes the estimated redshift distribution while $p_{i}(z)$ is the underlying true distribution. The parameters $\Delta z_{i}$ account for shifts in the means of the distributions and changes to their widths are parameterized through $z_{w, i}$. The quantity $z_{c}$ is kept constant in our analysis and is set to the redshift at which $\hat{p}_{i}(z)$ attains its maximal value. The normalization of the redshift distribution $p_{i}(z)$ depends on both $\Delta z_{i}$ and $z_{w, i}$ and we do not account for it in Eq.~\ref{eq:photo-z-model} for clarity.

@@

    \subsubsection{Robustness to photometric redshift uncertainties}
      One of the most important potential systematics in photometric galaxy clustering analyses are photometric redshift uncertainties and we therefore test the stability of our results to photo-$z$s in several different ways, as described in detail below.

>>>>

  \subsubsection{Photometric redshift systematics modeling}\label{sssec:methods.theory.photoz_syst}
    Uncertainties in photometric redshifts represent one of the major systematic uncertainties in photometric galaxy clustering analyses. \rev{In this work, we choose to model photo-$z$ errors as causing shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies\footnote{We note our photo-$z$ error model does not take into account the effect of catastrophic outliers but we do test for the presence of this systematic in Sec.~\ref{sec:photoz}.}. This allows us to parametrize the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by}
    \begin{equation}
      p_{i}(z) \propto \hat{p}_{i}(z_{c} + (1 + z_{w, i})(z-z_{c}) + \Delta z_{i}),
      \label{eq:photo-z-model}
    \end{equation} 
    where the index $i$ runs over the number of redshift bins considered in our analysis. In the above equation, $\hat{p}_{i}(z)$ denotes the estimated redshift distribution while $p_{i}(z)$ is the underlying true distribution. The parameters $\Delta z_{i}$ account for shifts in the means of the distributions and changes to their widths are parameterized through $z_{w, i}$. The quantity $z_{c}$ is kept constant in our analysis and is set to the redshift at which $\hat{p}_{i}(z)$ attains its maximal value. The normalization of the redshift distribution $p_{i}(z)$ depends on both $\Delta z_{i}$ and $z_{w, i}$ and we do not account for it in Eq.~\ref{eq:photo-z-model} for clarity.

@@

    \subsubsection{Robustness to photometric redshift uncertainties}\label{sec:photoz}
      One of the most important potential systematics in photometric galaxy clustering analyses are photometric redshift uncertainties and we therefore test the stability of our results to photo-$z$s in several different ways, as described in detail below.
